---
title: "Predicting Comment Likes on the Jubilee Middle Ground video 'Are We Allies? Black Americans vs Asian Americans'"
subtitle: |
  | Final Project 
  | Data Science 2 with R (STAT 301-2)
author: "Celena Kim"
date: today

format:
  html:
    toc: true
    embed-resources: true
    
execute:
  echo: false
  warning: false

from: markdown+emoji 
reference-location: margin
citation-location: margin
---

```{r}
#| label: basic-setup

# load packages ----
library(tidyverse)
library(tidymodels)
library(here)
library(doMC)
library(knitr)

# handle common conflicts
tidymodels_prefer()

# load data
allies <- read_rds("data/allies.rds")

# load training data/fits
load(here("data_splits/allies_split.rda"))
load(here("results/lm_fit_recipe3.rda"))
load(here("results/null_fit_recipe1.rda"))

# load pre-processing/feature engineering/recipe
load(here("recipes/recipe1_kitchen_sink.rda"))
load(here("recipes/recipe2_kitchen_sink_trees.rda"))
load(here("recipes/recipe3_transformed_interactions.rda"))
load(here("recipes/recipe4_transformed_trees.rda"))
```

::: {.callout-tip icon="false"}
## Github Repo Link

[Celena Kim Repo Link](https://github.com/stat301-2-2024-winter/final-project-2-celenakim)
:::

## Introduction

The data that I chose for my project was derived from gathering data on the psychological analysis of comments under the Jubilee video titled [Are We Allies? Black Americans vs Asian Americans \| Middle Ground](https://www.youtube.com/watch?v=pXo2ub_nZFc) found on [YouTube](https://www.youtube.com). This video features a poignant discussion between East Asian Americans and Black Americans, highlighting the conflict and tension present between these groups. As I am a part of the Social Cognition and Intergroup Processes Lab on campus, I thought it would be really interesting to combine social psych with data science to explore topics on bias and race through quantitative analysis. Therefore, I decided to explore the comments under this video by utilizing the software LIWC[^1], a text analysis program that can categorize text by the overall emotion they convey. Each comment under the video was analyzed and given a score of how much they communicate each various emotions/categories such as anger, clout, affiliation, power, assent, insight, sad, etc. After creating this data set, I ended up with 15,397 observations of comments and 51 variables, 46 of which are my predictor variables.

[^1]: an explanation of how this software works can be found [here](https://www.liwc.app/help/howitworks)

My predictive research question is: **How many likes does a comment on the Jubilee video "Are We Allies? Black Americans vs Asian Americans \| Middle Ground" receive?**

This is a regression problem with the target variable being the like count of a comment. The predictors are the LIWC emotional categories, as well as a categorical variable of the length of a comment (short, medium, or long).

This prediction model is useful because it could provide insights into the factors of emotional content and comment length that influence the engagement of comments on the Jubilee video. For content creators such as Jubilee, this prediction could inform their strategies for knowing what types of comments resonate with their audience in order to optimize their engagement. 

## Data Overview
### Response variable analysis:
```{r}
#| label: fig-likes-exploration
#| fig-cap: An exploration of the response variable, the like count of a comment.

ggplot(allies, aes(x = likes)) +
  geom_density() +
  labs(title = "Distribution of Likes",
       subtitle = "The variable is skewed right, with extreme outliers.",
       x = "Likes",
       y = "Density") +
  theme_minimal()
```
As seen in @fig-likes-exploration, the distribution of comment likes is heavily skewed to the right as there seems to be extreme high outliers. Thus, a transformation may be necessary to help normalize the distribution.

```{r}
#| label: fig-likes-transformed
#| fig-cap: An exploration of likes with a log transformation.

ggplot(allies, aes(x = log10(likes))) +
  geom_density() +
  labs(title = "Distribution of Likes with a Log Transformation",
       subtitle = "The variable is still skewed right, and many values were removed.",
       x = "Likes",
       y = "Density") +
  theme_minimal()
```
@fig-likes-transformed shows that a log transformation did seem to help to slightly normalize the likes distribution, but as there are numerous values of 0 within the observations, those values were removed. Therefore, I will instead transform the comment likes using a Yeo-Johnson transformation within my recipes. 

```{r}
#| label: fig-likes-yj
#| fig-cap: An exploration of likes with a log transformation.

ggplot(allies_train, aes(x = likes_yj)) +
  geom_density() +
  labs(title = "Distribution of Likes with a Yeo-Johnson Transformation",
       subtitle = "The variable is more normalized than before.",
       x = "Likes",
       y = "Density") +
  theme_minimal()
```
As can be seen in @fig-likes-yj, while the distribution of the number of likes on a comment is not perfectly normalized after undergoing a Yeo-Johnson transformation, it is still much less skewed than before.

### Data inspection:
```{r}
#| label: fig-allies-inspection
#| fig-cap: An inspection of the allies data set for missingness.

missing_counts <- colSums(is.na(allies))

missing_counts_df <- data.frame(Missing_Count = missing_counts)

kable(missing_counts_df)

```
After inspecting the allies data set for missingness, @fig-allies-inspection shows that there only seems to be missingness in the ID of a comment's parent comment. However, this does not seem to pose a significant issue, as this variable is not going to be important for my analysis.

### Categorical variable inspection:
```{r}
#| label: fig-cat-inspection
#| fig-cap: An inspection of the distribution of comment lengths.

ggplot(allies, aes(x = factor(comment_length, 
                              levels = c("short", 
                                         "medium", "
                                         long")))) +
  geom_bar() +
  labs(x = "Comment Length",
       y = "Count",
       title = "Distribution of Comment Length",
       subtitle = "There are significantly more short comments than long or medium.") +
  theme_minimal()
```
As visualized by @fig-cat-inspection, there seems to be a class imbalance within the categorical variable of comment length, as there are significantly more short comments than long or medium. Thus, it may be necessary to use stratified sampling, as this is effective in keeping the outcome distributions similar between the training and testing data sets.

### Predictor Variables Exploration
```{r}
#| label: fig-rest-raw-inspection
#| fig-cap: An inspection of the distributions of the numerical predictor variables.

allies_train_portion <- allies_train |> 
  slice_sample(prop = 0.8)

ggplot(allies_train_portion, aes(x = anger)) +
  geom_density() +
  labs(title = "Distribution of Anger",
       subtitle = "The variable is heavily skewed right",
       x = "Anger",
       y = "Density") +
  theme_minimal()
```
Just as the target variable of comment likes was heavily skewed right, the numerical predictor variables are all skewed in the same fashion, similarly to the emotional category of anger shown in @fig-rest-raw-inspection. Thus, these variables will also undergo a Yeo-Johnson transformation with a recipe step. 


### Predictor Variable Relationships:
```{r}
#| label: fig-cor-1
#| fig-cap: A visualization of the relationship between negative emotion and sadness.

allies_train_portion |>
  ggplot(aes(x = neg_emo,
             y = sad)) +
  geom_point() +
  labs(x = "Negative Emotion",
       y = "Sadness",
       title = "Sadness vs. Negative Emotion",
       subtitle = "There is a positive correlation.") +
  theme_minimal()
```

```{r}
#| label: fig-cor-2
#| fig-cap: A visualization of the relationship between negative emotion and anger

allies_train_portion |>
  ggplot(aes(x = neg_emo,
             y = anger)) +
  geom_point() +
  labs(x = "Negative Emotion",
       y = "Anger",
       title = "Anger vs. Negative Emotion",
       subtitle = "There is a positive correlation.") +
  theme_minimal()
```

```{r}
#| label: fig-cor-3
#| fig-cap: A visualization of the relationship between positive emotion and words that express achievement.

allies_train_portion |>
  ggplot(aes(x = pos_emo,
             y = achieve)) +
  geom_point() +
  labs(x = "Positive Emotion",
       y = "Achievement",
       title = "Achievement vs. Positive Emotion",
       subtitle = "There is a positive correlation.") +
  theme_minimal()
```

```{r}
#| label: fig-cor-4
#| fig-cap: A visualization of the relationship between displays of cognitive processes and displays of insight.

allies_train_portion |>
  ggplot(aes(x = cog_proc,
             y = insight)) +
  geom_point() +
  labs(x = "Cognitive Processes",
       y = "Insight",
       title = "Insight vs. Cognitive Processes",
       subtitle = "There is a positive correlation.") +
  theme_minimal()
```

```{r}
#| label: fig-cor-5
#| fig-cap: A visualization of the relationship between displays of affiliation and drives.

allies_train_portion |>
  ggplot(aes(x = affiliation,
             y = drives)) +
  geom_point() +
  labs(x = "Affiliation",
       y = "Drives",
       title = "Drives vs. Affiliation",
       subtitle = "There is a positive correlation.") +
  theme_minimal()
```
In order to determine possible relationships between the numerical variables, I created scatterplots of several pairs of predictor variables and examined their correlations. @fig-cor-1 - @fig-cor-5 show the variable pairs that seem to have the strongest positive correlations: negative emotion & sadness, negative emotion & anger, positive emotion & achievement, cognitive processes & insight, and affiliation & drives. Identifying these relationships is useful for adding interaction terms to my models as they will be able to capture the joint effect of two variables on the outcome variable of comment likes.

## Methods

methods...

## Model Building & Selection

model building & selection...

## Final Model Analysis

final model analysis...

## Conclusion

conclusion...

## References

"Are We Allies? Black Americans vs Asian Americans \| Middle Ground" *YouTube*, uploaded by Jubilee, 17 January 2021, [https://www.youtube.com/watch?v=pXo2ub_nZFc](https://www.youtube.com/watch?v=pXo2ub_nZFc).

LIWC, [https://www.liwc.app/](https://www.liwc.app/).

## Appendix: technical info about the data clean-up process


## Appendix: EDA

