---
title: "Progress Memo 1"
subtitle: |
  | Final Project 
  | Data Science 2 with R (STAT 301-2)
author: "Celena Kim"
date: today

format:
  html:
    toc: true
    embed-resources: true
    
execute:
  echo: true
  warning: false

from: markdown+emoji 
reference-location: margin
citation-location: margin
---

::: {.callout-tip icon="false"}
## Github Repo Link

[Celena Kim Repo Link](https://github.com/stat301-2-2024-winter/final-project-2-celenakim)
:::

## Data source & Why this Data

The data that I chose for my project was derived from gathering data on the psychological analysis of comments under the Jubilee video titled [Are We Allies? Black Americans vs Asian Americans \| Middle Ground](https://www.youtube.com/watch?v=pXo2ub_nZFc) found on [YouTube](https://www.youtube.com). This video features a poignant discussion between East Asian Americans and Black Americans, highlighting the conflict and tension present between these groups. As I am a part of the Social Cognition and Intergroup Processes Lab on campus, I thought it would be really interesting to combine social psych with data science to explore topics on bias and race through quantitative analysis. Therefore, I decided to explore the comments under this video through this project.

Using Python code, I first extracted each comment and its details such as like count and number of replies and put them into a spreadsheet. Then, utilizing the software LIWC[^1], a text analysis program that can categorize text by the overall emotion they convey, each comment was analyzed and given a score of how much they communicate each of 49 various emotions/categories such as anger, clout, affiliation, power, assent, insight, sad, etc.

[^1]: an explanation of how this software works can be found [here](https://www.liwc.app/help/howitworks)

## Data quality & complexity check

```{r}
library(tidyverse)
allies_data <- read_csv("/Users/celenakim/Desktop/
                        stat 301-2/final-project-2-celenakim/
                        data/raw/allies_video_data.csv")
```

The data set that I created from the steps highlighted in the previous section is called `allies_data`. The raw data set contains 15,398 observations and 66 variables. Of these variables, there are 7 categorical and 59 numerical. There only seems to be missingness in the "P" variable, which corresponds to the ID of the parent comment. This does not seem to pose a significant issue, as this variable is not going to be important for my analysis.

## Potential data issues

The biggest issue I see with my data is that the variable names regarding the basic details of the comments ("replies", "like_count", etc.) did not get copied over from the first spreadsheet and were thus replaced with letters A-P, so I will have to go back in and add those variable names once I clean this data set. Additionally, I may have to rename some of the emotion categories, as they may not be clear based on how they are named by LIWC.

## Prediction Problem
My predictive research question is: What categories of emotion communicated through a comment lead to the most likes on that comment?

This is a regression problem as I would like to predict a numerical outcome- the number of likes on a comment- and the target variable is the like count of a comment (variable "H" which will later be renamed to "like_count"). The predictors will be the emotional categories from LIWC. I also plan to create a categorical variable called "comment_length" that categories a comment based on a length of "one word", "short" (1-3 sentences), or "long" (4+ sentences).

This prediction model would be useful in determining what types of comments under a YouTube video are more likely to garner more attention/popularity. I think it would be very interesting to see overall the psychological implications of a comment's emotional makeup and its engagement.

## Target variable analysis

```{r}
# allies_data |> 
#   ggplot(aes(x = H)) +
#   geom_histogram() +
#   xlim(0, 9000) +
#   ylim(0, 100)
``` 
A univariate analysis of the target variable of comment like count (`H`) reveals that the distribution is skewed right. This means that a transformation may be necessary through means of log or square root transformation. There does not appear to be any missing values.

## Misc

Students are encouraged to add any other information that they think would be useful to communicate about their data and their plan. Articulating a time line would be a good idea since fitting/training the models may take more time than expected (leave adequate time to train models and then analyze).

